---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
require(eurostat)
require(dplyr)
require(ggplot2)
require(badgecreatr)
```

```{r badge, results='markup', eval=FALSE, include=FALSE}
dynamic_badges_minimal(license = "MIT")
```

# satellitereport

<!-- badges: start -->
[![Project Status: Concept – Minimal or no implementation has been done yet, or the repository is only intended to be a limited example, demo, or proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)[![license](https://img.shields.io/github/license/mashape/apistatus.svg)](https://choosealicense.com/licenses/mit/)[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)

<!-- badges: end -->

The goal of satellitereport is to facilitate cooperation with [satellitereport.com](satellitereport.com)

## Installation

You can install the satellitereport from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("antaldaniel/satellitereport")
```
## Example

This is how you create a choropleth map.

```{r choropleth }
library(satellitereport)
require(eurostat)
require(dplyr)
require(ggplot2)

all_geo_codes <- unique(eurostat::regional_changes_2016$code16)
all_geo_codes <- all_geo_codes [!is.na(all_geo_codes)]

test_intervals <- data.frame (
  geo = all_geo_codes,
  values = rnorm(length(all_geo_codes), mean = 50, sd = 15),
  row.names = NULL
)

create_choropleth ( dat = test_intervals,
                    geo_var = 'geo', values_var='values',
                    na_color = 'grey93', unit_text = 'unit', 
                    level=2, n=5, style ='kmeans') +
  ggplot2::labs( title = "Random Numbers Over NUTS-2 Regions", 
                 subtitle = "This is a demonstration of the function",
                 caption = "This is the caption text")


```


## Code of Conduct

Please note that the 'satellitereport' package is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.

